Linting Linearity in Core/System FC

### 2022-11-08 proposal.tex
Add more examples

\documentclass{article}

@@

\begin{document}

\maketitle

@@

@@

>>>>

\documentclass[10pt, a4paper, draft]{article}

@@

\begin{document}
\maketitle

@@

\subsection{Recursive Lets}

Optimisations can create a letrec which uses a variable linearly. The following
example uses 'x' linearly, but this is not seen by the linter.
\begin{code}

letrec f True = f False
       f False = x
in f True
\end{code}

Plan: make let-bound variables remember the usage environment.
See ticket #18694.

\subsection{Empty Case}

\begin{itemize}
\item https://gitlab.haskell.org/ghc/ghc/-/issues/20058
\item https://gitlab.haskell.org/ghc/ghc/-/issues/18768
\end{itemize}

\begin{code}
{-# LANGUAGE LinearTypes, EmptyCase #-}
module M where

{-# NOINLINE f #-}
f :: a %1-> ()
f x = case () of {}
\end{code}

@@

\begin{code}
data SBool :: Bool -> Type where
  STrue :: SBool True
  SFalse :: SBool False

type family If b t f where
  If True t _ = t
  If False _ f = f

dep :: SBool b -> Int %(If b One Many) -> Int
dep STrue x = x
dep SFalse _ = 0
\end{code}
